### 2024-06-02 2024-5-13/sections/heuristic.tex
fix the syntax error in heuristics

Moreover, propose a method to prune the search space further. Let $i \in [n]$. Suppose that during the search process for $\cB_i$, let $q$ be the current state of $\cB_i$ and $\lambda_i$ record the remaining occurrences of transitions of $\cB_i$. We compute the set of transitions of $\cB_i$ that are reachable from the state $q$. Let $\cT_q$ denote this set. If $\{(q, a, q', \myvec{c}) \mid \lambda_i((q, a, q', \myvec{c})) > 0\} \not \subseteq \cT_q$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_i$ will be found and meanwhile the constraint on the number of transitions enforced by $\lambda_i$ is satisfied. Therefore, in this case, the search process for $\cB_i$ in this direction halts, and the search process is backtracked.

>>>>

Moreover, we propose a method to prune the search space further. Let $i \in [n]$. Suppose that during the search process for $\cB_i$, let $q$ be the current state of $\cB_i$ and $\lambda_i$ record the remaining occurrences of transitions of $\cB_i$. We compute the set of transitions of $\cB_i$ that are reachable from the state $q$. Let $\cT_q$ denote this set. If $\{(q, a, q', \myvec{c}) \mid \lambda_i((q, a, q', \myvec{c})) > 0\} \not \subseteq \cT_q$, then we know that it is impossible to continue the search process so that a string accepted by $\cB_i$ will be found and meanwhile the constraint on the number of transitions enforced by $\lambda_i$ is satisfied. Therefore, in this case, the search process for $\cB_i$ halts and is backtracked.
